\chapter{Results and Discussion}
\label{chap:evaluation}
We have already looked at the details of IaaS and how it works technically.
Now it's time to give you some insights how such cloud infrastructures are implemented in real life and how resources can be provided and used by the consumers. Therefore we want to illustrate some concrete representatives who are are operating as a successful IaaS provider in practice in the following chapter.

\section{Amazon Elastic Compute Cloud (Amazon EC2)}

\subsection{A first glance on Amazon's world}
Amazon EC2 is part of the big Cloud Platform of the famous and globally well-known internet company Amazon.com, Inc., namely Amazon Web Services (AWS). AWS started offering IT infrastructure services to businesses using this Cloud computing model already in 2006. Today it's probably the most popular representative in this kind of IT sector offering highly reliable, scalable and low-cost infrastructure platform in the cloud used by a huge number of businesses in currently 190 countries around the world. They emphasize and try to implement the several benefits Cloud computing brings with it. Consumers should avoid hight initial costs to get their infrastructure running, instead a variable cost model with a pay-as-you-go price model should make their work much more cost-effective. Furthermore setting up and maintaining infrastructure components should not be a common task businesses should care about. In contrast the focus should be set on the major issues regarding the concrete business and infrastructure capacity can be provided by AWS with just a click on-demand. AWS truly offers a broad variety of several different services distinguished by it's provided resource type. A typical key benefit someone often face when talking about and using AWS is the perfect interoperability of all the platform components comprising it. That's probably a major point what makes AWS so beloved by customers around the globe. Next to storage(Amazon S3) or networking (Amazon VPC) compute resources, managed by Amazon EC2 are essential to every business as these are the physical machines services need to be alive. [3]

\subsection{EC2 Insights}
Amazon EC2 is designed for web and system administrators to make their lives easier. It provides easy manageable compute capacity available in the cloud. Via a web interface the administrator can request more or less capacity with just a few clicks within minutes. Some more minutes later the required instances are fully set-up with the desires of the user and ready-to-go. This allows the user to scale up and down (which means renting more or compute capacity) on the fly depending on the current demand and without any need to configure them manually. To give this explanation further importance and motivate why Amazon EC2 is the right choice for so many businesses, we want to look at some key benefits this cloud technology introduces in contrast to buying just traditional dedicated hardware at the provider of your trust. 